%-------------------------
% Resume in Latex
% Author : Akshath Chaudhary
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem, calc}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand\small{\normalsize}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%-----------HEADING-----------
\begin{center}
    \textbf{\huge \scshape Akshath Chaudhary} \\ \vspace{1pt}
    \small (416)\,830-4337 $|$ \href{mailto:akshath.chaudhary@uwaterloo.ca}{\underline{akshath.chaudhary@uwaterloo.ca}} $|$ 
    \href{https://linkedin.com/in/akshathc01}{\underline{LinkedIn}} $|$
    \href{https://github.com/akshathc01}{\underline{Github}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{September 2019 -- May 2024}
      {4B, Bachelor of Computer Science}{Waterloo, ON}
      \begin{itemize}
%      \small\item \textbf{CGPA}: 3.90/4.00
      \small\item \textbf{Awards}: \textit{Dean's Honours List, Concept Entrepreneurship Funding Recipient, Intramural Soccer finalist}
      \small\item \textbf{Relevant Coursework}: \textit{Data Structures and Data Management, Machine Learning, Computer Security, Object-Oriented Software Development, Algorithm Design and Data Abstraction, Operating Systems}
      \end{itemize}
   \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Relevant Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
          {Google}{May 2023 -- August 2023}
          {Incoming Software Engineering Intern}{Toronto, ON}
          \resumeItemListStart
            \resumeItem{Joining the Technical Infrastructure team in Summer 2023 to build the backend infrastructure for GCP.}
           \resumeItemListEnd
  \resumeSubheading
      {Coinbase}{September 2022 -- December 2022}
      {Software Engineering Intern}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Launched a \textbf{low-latency endpoint} for hot wallets to interact with an internal ML feed engine using Go, Docker, and SQL which resulted in a 23\% faster retrieval time of ERC-20 token recommendations.}
        \resumeItem{Developed a \textbf{template engine} using Python to automate the configuration onboarding process for an internal feed engine with support for new candidate generators and rankers.}
        \resumeItem{Derived online and offline \textbf{features} for better personalized asset recommendations including features about the most recently purchased asset and the output of existing offline models.}
       \resumeItemListEnd
      
   \resumeSubheading
      {Lumafield}{January 2022 -- April 2022}
      {Software Engineering Intern}{San Francisco, CA}
       \resumeItemListStart
       \resumeItem{Developed a self-learning \textbf{recommendation engine} with collaborative filtering for initial scan settings per customer segment using TensorFlow, Pandas, and Matplotlib.}
       \resumeItem{Implemented a \textbf{language processing} algorithm to detect and match similar scans for easy analysis with a $k$-fold cross validated accuracy of 85\% using SciPy and NumPy.}
       \resumeItem{Constructed an ETL \textbf{pipeline} to concurrently update scan specific data in real-time which reduced wait time by 35\% and decreased storage consumption by 60\% using Dask, Kubernetes, and SQLAlchemy.}
       \resumeItemListEnd
    
    \resumeSubheading
      {Huawei}{May 2021 -- December 2021}
      {Software Engineering Intern}{Toronto, ON}
      \resumeItemListStart
	    \resumeItem{\textbf{Improved runtime} of FPGA Static Timing Analysis (STA) by over 88\% via a conditional incremental algorithm using Boost that identifies and updates modified elements in the netlist.}
        \resumeItem{Spearheaded development of a \textbf{testing framework} that increased code coverage by 120\% using CMake.}
	 \resumeItem{Implemented a \textbf{path delay validator} that estimates all point to point delays using node aggregation.}
      \resumeItemListEnd
      \vspace{0pt}
    \resumeItemListEnd
 


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
    	{\textbf{Taco} $|$ \emph{Python, React.js, Express,js, Firestore}}{June 2021}
          \resumeItemListStart
            \resumeItem{Implemented a unique quantitative speech analysis algorithm using GCP NLP, Express.js, and Firestore that returns a score based on the user's confidence, clarity, and syntax. Built the frontend using React. }
            \resumeItem{Declared as the \textbf{overall winner} of EngHacks 2021 and secured the first prize among \textbf{300+} hackers.}
          \resumeItemListEnd
    \resumeItemListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=10.8pt, label={}]
    \small{\item{
     \textbf{Languages}{: \hspace{1.5mm} Python, Go, \CC, SQL, C, Java, Ruby, JavaScript, HTML/CSS, R} \\
     }}
     \vspace{0pt}
      \small{\item{
     \textbf{Libraries}{:\hspace{6.2mm} TensorFlow, PyTorch, Pandas, NumPy, SciPy, MongoDB, Scikit, Boost \CC, Tatum} \\
     }}\vspace{0pt}
      \small{\item{
     \textbf{Tools}{:\hspace{13mm} Git, Docker, Kubernetes, VIM, GDB, GCOV/LCOV, TravisCI, Google Cloud Platform} \\
     }}\vspace{0pt}
      \small{\item{
     \textbf{Frameworks}{: React, Node.js, AWS, NLP, Postgres, FQS, OpenCV, Django, Angular.js, Vue.js} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
